---
name: Mark V.
surname: Murphy
profilepic: me.jpg
position: Data Analyst
address: Bradford, UK
# phone: 
# www: 
email: murphymv@gmail.com
twitter: murphy_mv
github: murphymv
linkedin: murphymv
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: I have >10 years' experience in processing, analysing, and communicating data, gained from education, employment, PhD research, and self-directed projects and training. I have a background in science, but with increasing interest and expertise in statistics, programming, and data science in recent years. I also have developing interests in AI, health, and finance, and in the role of technology in driving rapid societal change. I have a lifelong commitment to learning and development, and generally strive for high quality in everything I do. I enjoy applying my varied skills and experience to new challenges, ideally involving meaningful and impactful data-driven projects, products, and services. For further details of my previous experience, skills and outputs, see my [longer-form (academic) CV](https://github.com/murphymv/CV/blob/main/CV_academic.pdf).
output: vitae::twentyseconds
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
```

# Skills

## Existing:

-   Data Handling (CSVs, Excel, databases/SQL, cleaning, etc.)

-   Statistics and Modelling (regression, GLMMs, SEMs, validation, etc.)

-   Data Visualisation and Plotting (e.g. {ggplot2})

-   Programming (R -- analysis, functions, methods, optimisation, etc.)

-   Package Development and Version Control (R, Git/GitHub)

-   Code Documentation and Examples/Testing (R Markdown, Roxygen2)

-   Writing and Editing (vignettes, reports, theses, publications)

-   Communication (presentations, media, outreach)

-   Teamwork (fieldwork, group projects, workshops, collaborations)

-   Project Management (independent work, timelines, etc.)

## Learning:

-   Machine Learning (classification and clustering techniques, etc.)

-   Dashboards/Reports (Power BI, R Shiny)

-   Web/Document Styling (CSS, HTML)

-   Programming (Python, Julia)

# Projects

-   [This CV](https://github.com/murphymv/CV) (2021--): compiled using the R package {vitae}, and R Markdown, YAML, Pandoc, and LaTeX. Updated regularly.

-   [Machine Learning course](https://github.com/murphymv/Machine-Learning-A-Z) (2021--): Python and R code from [Udemy course](https://www.udemy.com/course/machinelearning/) compiled into a single R {bookdown} project for easy reference. Experimental.

-   [Forked R package {rscodeio](https://github.com/murphymv/rscodeio)} (2021--): extends RStudio VS Code dark theme (CSS) to Options menu and other IDE elements, R Markdown documents, and {pkgdown} and {bookdown} websites. Experimental.

-   [R package {dissCqN](https://murphymv.github.io/dissCqN/)} (2021--): compositional dissimilarity for species assemblages or interaction networks. `r paste0("v", paste(unlist(strsplit(paste(packageVersion("dissCqN")), "\\."))[1:3], collapse = "."), ".")`

-   [R package {semEff](https://murphymv.github.io/semEff/)} (2019--): effects and confidence intervals for 'piecewise' structural equation models (SEM). `r paste0("v", paste(unlist(strsplit(paste(packageVersion("semEff")), "\\."))[1:3], collapse = "."), ". CRAN downloads: ", round(sum(dlstats::cran_stats("semEff")$downloads) / 1000), "K.")`

-   Research collaborations (2018--): contributing statistical, programming, editing, and domain expertise to ecological projects (University of Western Australia, University of Leeds, Zhejiang University; publications pending).

# Experience

```{r}
exp <- tibble::tribble(
  ~ position, ~ year, ~ location, ~ employer,
  "Writing, Programming, Retraining, Career Change (w/ breaks)", "2018–22", "UK", "Self-Directed",
  "Research Assistant (Data Analysis, Bioinformatics)", "2016–18", "Perth, Australia", "University of Western Australia",
  "Lab Demonstrator (Student Assistance, Supervision)", "2016–16", "Perth, Australia", "University of Western Australia",
  "Research Assistant (GPS/GIS, Entomology)", "2011–11", "Perth, Australia", "University of Western Australia"
)
vitae::detailed_entries(exp, position, year, location, employer)
```

# Education

```{r}
edu <- tibble::tribble(
  ~ degree, ~ year, ~ where, ~ inst,
  "PhD (Ecology)", "2012–16", "Perth, Australia", "The University of Western Australia", 
  "MSc (Biodiversity and Conservation)", "2007–08", "Dublin, Ireland", "Trinity College Dublin",
  "BA (Zoology)", "2001–05", "Dublin, Ireland", "Trinity College Dublin"
)
vitae::detailed_entries(edu, degree, year, where, inst)
```

```{r, eval = FALSE, include = FALSE}
# create a publications.bib file first (export from Zotero)
pubs <- vitae::bibliography_entries("publications.bib")
dplyr::arrange(pubs, dplyr::desc(author$family), issued)
```
