---
name: Mark V.
surname: Murphy
profilepic: me.jpg
position: Data Analyst
address: Bradford, UK
# phone: +44 7542 368784
# www: 
email: murphymv@gmail.com
twitter: murphy_mv
github: murphymv
# linkedin: murphymv
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: I have >10 years experience in processing, analysing, and communicating data. My experience has been gained from education, employment, PhD research, and self-driven projects and training. I have a background in ecology and conservation, but with increasing interest and expertise in statistics, programming, and data science in recent years. I also have developing interests in the areas of AI, health, and finance (esp. cryptocurrencies), and in the role of technology in driving rapid societal change. I am currently looking to apply my skills and experience to a new role, and ideally to meaningful data-driven projects and services with wider societal benefits. Further details on my previous experience, skills and outputs are in my [extended (academic) CV](https://github.com/murphymv/CV/CV_academic).
output: vitae::twentyseconds
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
```

# Skills

Existing:

-   Data Collection and Management (spreadsheets, CSVs)

-   Analysis and Modelling (regression, GLMs, mixed models, SEMs, etc.)

-   Visualisation and Plotting (e.g. `ggplot2`)

-   Programming (R --- functions, methods, iteration, parallelisation, etc.)

-   Code Documentation and Vignettes (`rmarkdown`, `roxygen2`)

-   Package Development and Version Control (R, Git/GitHub)

-   GIS, Digital Mapping, and Spatial Analysis (QGIS, ArcGIS, R)

-   Writing and Editing (reports, theses, publications)

-   Communication (seminars, workshops, media, teamwork, supervision)

Learning:

-   Machine Learning

-   Web/Document Styling (CSS, html)

-   Dashboards (e.g. `shiny`)

-   Programming (Python, Julia, SQL)

# Projects

-   [This CV](https://github.com/murphymv/CV) (2021---): compiled using `rmarkdown`, `pandoc`, and `LaTeX`.

-   [Fork of R package `rscodeio`](https://github.com/murphymv/rscodeio) (2021---): extends RStudio VS Code dark theme to options menu and other elements, `rmarkdown` documents, `pkgdown` websites. Experimental.

-   [R package `dissCqN`](https://github.com/murphymv/dissCqN) (2021---): calculate C~*qN*~ compositional dissimilarity for biotic assemblages or interaction networks. v0.1.0. CRAN submission pending.

-   [R package `semEff`](https://github.com/murphymv/semEff) (2019---): calculate effects and confidence intervals for 'piecewise' structural equation models (SEM). v0.5.0. CRAN downloads \>15k (\>2k/month). New release pending (v0.6.0).

-   Bioinformatics (2019---): editing and submission of hundreds of digital DNA sequences and metadata to the Barcode of Life Database. Published subset [here](https://doi.org/10.5883/ds-aglswa).

-   Research (2018---): contributing statistical, programming, and other expertise to collaborative ecological research projects (University of Western Australia, University of Leeds; publications to follow).

# Experience

```{r}
exp <- tibble::tribble(
  ~ position, ~ year, ~ location, ~ employer,
  "Projects, Retraining, Career Change (incl. health breaks)", "2018—21", "UK", "Self-Driven", 
  "Research Assistant (Data Analysis, Bioinformatics)", "2016—18", "Perth, Australia", "University of Western Australia", 
  "PhD (Ecology)", "2012—16", "Perth, Australia", "University of Western Australia",
  "Research Assistant (GIS, Insect Taxonomy)", "2011—11", "Perth, Australia", "University of Western Australia",
)
vitae::detailed_entries(exp, position, year, location, employer)
```

# Education

```{r}
edu <- tibble::tribble(
  ~ degree, ~ year, ~ where, ~ inst,
  "PhD in Ecology", "2012—16", "Perth, Australia", "The University of Western Australia", 
  "MSc in Biodiversity and Conservation", "2007—08", "Dublin, Ireland", "Trinity College Dublin", 
  "BA in Zoology", "2001—05", "Dublin, Ireland", "Trinity College Dublin"
)
vitae::detailed_entries(edu, degree, year, where, inst)
```

```{r, eval = FALSE, include = FALSE}
# create a publications.bib file first (export from Zotero)
pubs <- vitae::bibliography_entries("publications.bib")
dplyr::arrange(pubs, dplyr::desc(author$family), issued)
```
