---
name: Mark V.
surname: Murphy
profilepic: me.jpg
position: Data Analyst
address: Leeds, UK
# phone: 
# www: 
email: murphymv@gmail.com
twitter: murphy_mv
github: murphymv
linkedin: murphymv
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: I have almost 20 years' experience in data management, analysis, and communication -- gained from education, employment, PhD research, and self-directed projects and training. My background is in the biological sciences, but with increasing interest and expertise in statistics, programming, data science, AI, and health sciences in recent years. I have a lifelong commitment to learning and development, and generally strive for high quality in everything I do. I enjoy applying my skills and experience to new challenges, ideally involving meaningful and impactful data-driven projects, products, and services. For additional details of my previous experience, skills and outputs, see my [longer-form (academic) CV](https://github.com/murphymv/CV/blob/main/CV_academic.pdf).
output: vitae::twentyseconds
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
```

# Skills

-   Databases/Data Management (SQL Server, Cosmos DB, OneLake, Excel)

-   Statistics/Machine Learning (R {tidymodels}, Synapse Data Science)

-   Data Visualisation and Plotting (Power BI, R {ggplot2})

-   Dashboards and Reports (Power BI)

-   Programming (R, SQL, M, DAX)

-   Code Documentation and Testing (scripts, notebooks, web)

-   Library Development (R)

-   Source Control (Git, GitHub, Azure DevOps)

-   Cloud Storage and Computing (Azure, MS Fabric, Apache Spark)

-   Web and Document Styling (CSS, HTML, YAML)

-   Writing and Editing (documentation, reports, publications)

-   Communication and Teamwork

-   Project Management

-   Stakeholder Engagement

-   Business Processes

# Technical Projects

-   [This CV](https://github.com/murphymv/CV) (2021--): compiled using the R library {vitae}, via R Markdown, YAML, Pandoc, and LaTeX.

-   [ML Course Documentation](https://github.com/murphymv/Machine-Learning-A-Z) (2021--): Python and R scripts from a [Udemy course](https://www.udemy.com/course/machinelearning/) collected in a single 'book' format (R {bookdown} project) for easy reference. Experimental.

-   [R Library {rscodeio} (fork)](https://github.com/murphymv/rscodeio) (2021--): extension of an RStudio dark theme (CSS) to additional IDE elements, R Markdown documents, and websites (R {pkgdown}, {bookdown}). Experimental.

-   [R Library {dissCqN}](https://murphymv.github.io/dissCqN/) (2021--): compositional dissimilarity for species assemblages or interaction networks. `r paste0("v", paste(unlist(strsplit(paste(packageVersion("dissCqN")), "\\."))[1:3], collapse = "."), ". CRAN downloads: ", round(sum(dlstats::cran_stats("dissCqN")$downloads) / 1000), "K.")`

-   [R Library {semEff}](https://murphymv.github.io/semEff/) (2019--): effects and confidence intervals for 'piecewise' structural equation models (SEM). `r paste0("v", paste(unlist(strsplit(paste(packageVersion("semEff")), "\\."))[1:3], collapse = "."), ". CRAN downloads: ", round(sum(dlstats::cran_stats("semEff")$downloads) / 1000), "K.")`

# Experience

```{r}
tibble::tribble(
  ~ position, ~ year, ~ location, ~ employer,
  "Data Analyst", "2022-23", "Leeds, UK", "Optima Health",
  "Research Writing/Technical Projects/Retraining", "2018–22", "Leeds, UK", "Self-Directed",
  "Research Assistant: Bioinformatics/Data Analysis", "2016–18", "Perth, Australia", "University of Western Australia",
  "Lab Demonstrator: Student Assistance/Supervision", "2016–16", "Perth, Australia", "University of Western Australia",
  # "Research Assistant (GPS/GIS, Entomology)", "2011–11", "Perth, Australia", "University of Western Australia"
) |> 
  vitae::detailed_entries(position, year, location, employer)
```

# Education

```{r}
tibble::tribble(
  ~ degree, ~ year, ~ where, ~ inst,
  "PhD (Ecology)", "2012–16", "Perth, Australia", "The University of Western Australia", 
  "MSc (Biodiversity and Conservation)", "2007–08", "Dublin, Ireland", "Trinity College Dublin",
  "BA (Zoology)", "2001–05", "Dublin, Ireland", "Trinity College Dublin"
) |> 
  vitae::detailed_entries(degree, year, where, inst)
```

```{r, eval = FALSE, include = FALSE}
# # create a publications.bib file first (export from Zotero)
# vitae::bibliography_entries("publications.bib") |> 
#   dplyr::arrange(dplyr::desc(author$family), issued)
```
