---
name: Mark V.
surname: Murphy
profilepic: me.jpg
position: Data Analyst
address: Bradford, UK
# phone: +44 7542 368784
# www: 
email: murphymv@gmail.com
twitter: murphy_mv
github: murphymv
# linkedin: murphymv
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: I have >10 years experience in processing, analysing, and communicating data, gained from education, employment, PhD research, and self-directed projects and training. I have a background in science (ecology), but with increasing interest and expertise in statistics, programming, and data science in recent years. I also have developing interests in AI, health, and finance (esp. cryptocurrencies), and in the role of technology in driving rapid societal change. I have a lifelong commitment to learning and development, and generally strive for high quality in everything I do. I am currently looking to apply my skills and experience to new challenges and a new role — ideally involving meaningful and impactful data-driven projects and services. For further details on my previous experience, skills and outputs, see my [longer-form (academic) CV](https://github.com/murphymv/CV/blob/main/CV_academic.pdf).
output: vitae::twentyseconds
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
```

# Skills

Existing:

-   Data Collection and Management (spreadsheets/CSVs, messy data, etc.)

-   Analysis and Modelling (regression, GLM(M)s, SEMs, validation, etc.)

-   Visualisation and Plotting (e.g. ggplot2)

-   Programming (R --- functions, methods, iteration, parallelisation, etc.)

-   Package Development and Version Control (R, Git/GitHub)

-   Code Documentation and Vignettes (R Markdown, Roxygen2)

-   Writing and Editing (reports, theses, publications)

-   Communication (presentations, media, outreach)

-   Teamwork (fieldwork, group projects, workshops, collaborations)

Learning:

-   Machine Learning

-   Web/Document Styling (CSS, html)

-   Dashboards/Web Apps (Shiny)

-   Programming (Python, Julia, SQL)

# Projects

-   [This CV](https://github.com/murphymv/CV) (2021---): compiled using R Markdown, YAML, Pandoc, and LaTeX.

-   [Forked R package rscodeio](https://github.com/murphymv/rscodeio) (2021---): extends RStudio VS Code dark theme to menus and other IDE elements, R Markdown documents, pkgdown websites. Experimental.

-   [R package dissCqN](https://murphymv.github.io/dissCqN/) (2021---): calculate compositional dissimilarity for species assemblages or interaction networks. v0.1.0. CRAN submission pending.

-   [R package semEff](https://murphymv.github.io/semEff/) (2019---): calculate effects and confidence intervals for structural equation models (SEM). v0.5.0. CRAN downloads \>15K (\~2K/month). New release pending (v0.6.0).

-   Bioinformatics (2019---): editing and submission of hundreds of digital DNA sequences and metadata to the [Barcode of Life Data System](https://www.boldsystems.org/). Published subset [here](https://doi.org/10.5883/ds-aglswa); more pending research publications.

-   Research (2018---): contributing statistical, editing, and domain expertise to ecological research projects (University of Western Australia, University of Leeds; publications to follow).

# Experience

```{r}
exp <- tibble::tribble(
  ~ position, ~ year, ~ location, ~ employer,
  "Data Projects, Training, Career Change (incl. health breaks)", "2018—21", "UK", "Self-Driven",
  "Research Assistant (Data Analysis, Bioinformatics)", "2016—18", "Perth, Australia", "University of Western Australia",
  "Lab Demonstrator (Student Assistance, Supervision)", "2016—16", "Perth, Australia", "University of Western Australia",
  "Research Assistant (GIS, Entomology)", "2011—11", "Perth, Australia", "University of Western Australia"
)
vitae::detailed_entries(exp, position, year, location, employer)
```

# Education

```{r}
edu <- tibble::tribble(
  ~ degree, ~ year, ~ where, ~ inst,
  "PhD (Ecology)", "2012—16", "Perth, Australia", "The University of Western Australia", 
  "MSc (Biodiversity and Conservation)", "2007—08", "Dublin, Ireland", "Trinity College Dublin",
  "BA (Zoology)", "2001—05", "Dublin, Ireland", "Trinity College Dublin"
)
vitae::detailed_entries(edu, degree, year, where, inst)
```

```{r, eval = FALSE, include = FALSE}
# create a publications.bib file first (export from Zotero)
pubs <- vitae::bibliography_entries("publications.bib")
dplyr::arrange(pubs, dplyr::desc(author$family), issued)
```
